Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
review conclusions

There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. This effectively allows
us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
plus the effects of numeric calculations in the engine.
Synthesised controllers using this verifier will always
be stable for all plants in the family.
% and only generate counterexamples when the precision of the
%engine is insufficient (\emph{ie} no stable plant could be found). 
Our preliminary experiments showed that a synthesis approach
using this verification engine has poor performance and we
%Given the high computational cost of this
%approach, 
therefore designed a second approach, which we describe below.
Our experimental results described in Section~\ref{sec:experiments}, 
%try both approaches and provide the time for the fastest. 
show that the speedup yielded by the second approach 
is in most cases of at least two orders of magnitude.

@@

A third set of benchmarks that consists of a physical plant for satellite
applications is considered~\cite{Franklin15}, in order to evaluate the
full capabilities of the present approach.  In particular, satellites often require
attitude (pose) control for proper orientation of antennas and sensors
w.r.t.~earth.  The satellite attitude control is typically used for
three-axis attitude tracking, but here only one axis at a time is
considered.  The motion equation for the one-axis system, despising
disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}

@@

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
seconds as measured by the UNIX date command.  For the approach using a
two-stage verification engine we apply a timeout of 8 hours per benchmark,
and 24 hours for the approach using an one-stage engine.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with an algorithm for verifying robust closed-loop stability, 
in order to compute a parametric solution for a digital controller given 
a continuous (or discrete) plant specification.  This enables us to automatically
synthesise correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.

>>>>

There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounds operations outwards during calculations. This effectively allows
us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
plus the effects of numeric calculations in the engine.
Synthesised controllers using this verifier will always
be stable for all plants in the family.
% and only generate counterexamples when the precision of the
%engine is insufficient (\emph{ie} no stable plant could be found). 
Our preliminary experiments showed that a synthesis approach
using this verification engine has poor performance and we
%Given the high computational cost of this
%approach, 
therefore designed a second approach, which we describe below.
Our experimental results described in Section~\ref{sec:experiments}, 
%try both approaches and provide the time for the fastest. 
show that the speedup yielded by the second approach 
is in most cases of several orders of magnitude.

@@

A third set of benchmarks that consists of a physical plant for satellite
applications is considered~\cite{Franklin15}, in order to evaluate the
present approach full capabilities.  In particular, satellites often require
attitude (pose) control for proper orientation of antennas and sensors
w.r.t.~earth.  The satellite attitude control is typically used for
three-axis attitude tracking, but here only one axis at a time is
considered.  The motion equation for the one-axis system, despising
disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}

@@

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
seconds as measured by the UNIX date command.  For the approach using a
two-stage verification engine we apply a timeout of 8 hours per benchmark,
and 24 hours for the approach using a one-stage engine.

@@

We have presented a CEGIS-based approach implemented in a tool called \tool, 
which uses inductive synthesis in conjunction with an algorithm for verifying 
robust closed-loop stability. In particular, \tool is able to compute a parametric solution 
for a stabilizing digital controller given a continuous (or discrete) plant 
specification.  This enables us to automatically synthesise correct-by-construction 
digital controllers for a given model of their physical environment.  
Our approach addresses the effects of the quantisers (A/D and D/A converters) 
as time discretisation elements with quantisation noise.  Our experimental results 
show that \tool is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems, including state-space representation.  
We will also consider performance requirements while
synthesising the digital controller.
